### 2023-11-29 manuscript.tex
Added returns after each panel caption for greater readability
Added alignment figure

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{conserved/out/alignment_glutamine.png}
\centering
\caption{\textbf{Example regions with significant and non-significant glutamine-associated features.}
\textbf{(A-B)} Scatter plot of the regions' log likelihood ratios against the estimated optimal value for the feature fraction\_Q and repeat\_Q, respectively.
\textbf{(C)} Alignment of disorder region from orthologous group 03BB. The colored bar on the left indicates the hexbins containing that region in panels A-B.
\textbf{(D)} Log likelihood ratios of features for the region in panel C. Critical values for 1 and 5\% type I error rates are shown with dotted lines.
\textbf{(E)} Alignment of disorder region from orthologous group 0715. The colored bar on the left indicates the hexbins containing that region in panels A-B.
\textbf{(F)} Log likelihood ratios of features for the region in panel E. Critical values for 1 and 5\% type I error rates are shown with dotted lines.}
\label{fig:alignment}
\end{figure}
